Digital History in Finland, 1488-1828

### 2015-12-08 inst/examples/20151209-HelsinkiDH.Rmd
ok

```{r 20151209-HDH-topg, echo=FALSE, message=FALSE, warning=FALSE, cache=FALSE, fig.height=5, fig.width=8}
topg <- setdiff(names(rev(sort(table(dfo$gatherings))))[1:6], "NA")
dfs <- dfo %>%
    filter(gatherings %in% topg & publication_year > 1650) %>%
    group_by(publication_decade, gatherings) %>% tally()
dfs$gatherings <- order_gatherings(dfs$gatherings)    
p <- ggplot(dfs, aes(x = publication_decade, y = n, color = gatherings)) + geom_point(size = 3) + geom_smooth(fill = "lightgray", size = 2, alpha = 0.2) + ggtitle("Top gatherings timeline") + ylim(c(0, max(dfs$n))) + xlab("Publication decade") + ylab("Title count (n)")
print(p)
```

>>>>

```{r 20151209-HDH-topg, echo=FALSE, message=FALSE, warning=FALSE, cache=FALSE, fig.height=5, fig.width=9}
topg <- setdiff(names(rev(sort(table(dfo$gatherings))))[1:6], "NA")
dfs <- dfo %>%
    filter(gatherings %in% topg & publication_year > 1650) %>%
    group_by(publication_decade, gatherings) %>% tally()
dfs$gatherings <- order_gatherings(dfs$gatherings)    
p <- ggplot(dfs, aes(x = publication_decade, y = n, color = gatherings)) + geom_point(size = 3) + geom_smooth(fill = "lightgray", size = 2, alpha = 0.2) + ggtitle("Top gatherings timeline") + ylim(c(0, max(dfs$n))) + xlab("Publication decade") + ylab("Title count (n)")
print(p)
```
